Testing and Isolation Efficacy:\\Insights from a Simple Epidemic Model

### 2021-06-24 SIR_manuscript.tex
flowchart was editted

Analytic calculation of the next-generation matrix and simplification of the $\Rnum$ expression, were performed in Maple\textsuperscript{\texttrademark} \citep{maple14}; numerical calculation and contour plots were done in R \citep{r}.
We computed the values and contours of $\Delta$ at both low (\fref{pan}) and high (\fref{pan2}) testing intensities, and for both random testing ($w_S=w_I=w_R=1$) and targeted testing ($w_S=0.3$; $w_I=w_R=1$). Because it is expressed as a proportion of $\Rnum$, the effectiveness of control $\Delta$ is (at least in the $\rho \ll 1$ case, Eq.~\ref{lin}) independent of the transmission rate $\beta$, and hence of $\Rnum$ in the case where we vary $\Rnum$ by changing the transmission rate for a fixed generation interval.

>>>>

Analytic calculation of the next-generation matrix and simplification of the $\Rnum$ expression, were performed in Maple\textsuperscript{\texttrademark} \citep{maple14}; numerical calculation and contour plots were done in R \citep{r}.
We computed the values and contours of $\Delta$ at both low (\fref{pan}) and high (\fref{pan2}) testing intensities, and for both random testing ($w_S=w_I=w_R=1$) and targeted testing ($w_S=0.3$; $w_I=w_R=1$). Because it is expressed as a proportion of $\Rnum$, the effectiveness of control $\Delta$ is (at least in the $\rho \ll 1$ case, Eq.~\ref{eq:lin}) independent of the transmission rate $\beta$, and hence of $\Rnum$ in the case where we vary $\Rnum$ by changing the transmission rate for a fixed generation interval.
